Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-06 paper/intro.tex
Paper update

The Bayesian optimization algorithm has been extended to enable batch
selection. Some prior works, like the qEI\cite{qEI}, qKG\cite{wu2016parallel}
and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
approaches, consider to search for the optimal batch selection for a given
acquisition function. These methods usually involve some approximations or
Monte-Carlo sampling, and thus scales poorly as the batch size increases. Other
works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
batch-UCB(BUCB, BLCB for minimization
problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
exploration (GP-UCB-PE)~\cite{contal2013parallel} method and the local
penalization~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
strategies that select individual points until the batch is filled.

% TODO: Beiefly introduce my algorithm
All the algorithms mentioned above choose to use single acquisition function,
and except for the simulation matching method and local penalization method
which can select arbitrary acquisition function, other parallelization methods
rely on a specific acquisition function. The UCB acquisition function must be
used for BUCB and GP-UCB-PE, and the knowledge gradient method must be used for
the qKG algorithm. As is stated in~\cite{hoffman2011portfolio}, no single
acquisition function can always outperform other acquisition functions, relying
on one acquisition function may result in poor performance.

In this paper, we propose to parallelize the Bayesian optimization algorithm
via the multi-objective acquisition ensemble (MACE). Firstly, in each
iteration, after the GP model is updated, multiple acquisition functions are
selected, we then perform multi-objective optimization to find the \emph{Pareto
front} (PF) of the acquisition functions. The PF represents the best trade-off
between these acquisition functions. When batch evaluations are possible, we
can sample multiple points on the optimized PF to accelerate the optimization.

The MACE algorithm is tested using several analytical benchmark functions and
two real-world analog circuits, including an operational amplifier with ten
design parameters and a class-E power amplifier with twelve design parameters.
The BLCB method, local penalization method with expected improvement
acquisition function (EI-LP), qEI methods and qKG methods are compared with
MACE. The proposed MACE method achieved competitive performance when compared
with the listed state-of-the-art algorithms.

>>>>

The Bayesian optimization algorithm has been extended to enable batch
selection. Some prior works, like the qEI\cite{qEI}, qKG\cite{wu2016parallel}
and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
approaches, consider to search for the optimal batch selection for a given
acquisition function. These methods usually involve some approximations or
Monte-Carlo sampling, and thus scales poorly as the batch size increases. Other
works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
batch-UCB(BUCB, BLCB for minimization
problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
exploration (GP-UCB-PE)~\cite{contal2013parallel} method and the local
penalization (LP)~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
strategies that select individual points until the batch is filled.

% TODO: Beiefly introduce my algorithm
All the algorithms mentioned above choose to use single acquisition function,
and except for the SM method and LP method which can use arbitrary acquisition
function, other parallelization methods rely on a specific acquisition
function. The UCB acquisition function must be used for BUCB and GP-UCB-PE, and
the knowledge gradient method must be used for the qKG algorithm. As is stated
in~\cite{hoffman2011portfolio}, no single acquisition function can always
outperform other acquisition functions, relying on one acquisition function may
result in poor performance.

In this paper, we propose to parallelize the Bayesian optimization algorithm
via the multi-objective acquisition ensemble (MACE). The proposed MACE method
exploits the disagreement between different acquisition functions to enable
parallel selection. At each iteration, after the GP model is updated, multiple
acquisition functions are selected, we then perform multi-objective
optimization to find the \emph{Pareto front} (PF) of the acquisition functions.
The PF represents the best trade-off between these acquisition functions. When
batch evaluations are possible, we can sample multiple points on the optimized
PF to accelerate the optimization.

The MACE algorithm is tested using several analytical benchmark functions and
two real-world analog circuits, including an operational amplifier with ten
design parameters and a class-E power amplifier with twelve design parameters.
The BLCB method, local penalization method with expected improvement
acquisition function (EI-LP), qEI methods and qKG methods are compared with
MACE. The proposed MACE method achieved competitive performance when compared
with the state-of-the-art algorithms listed in the paper.
